---
title: "R script of Data-driven Regularized Adaptive Risk Forecasting Oct26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```


```{r}
rm(list=ls(all=TRUE)) # Remove objects from environment
```


\section{Install and load package}

```{r}
# Load required packages
library(zoo)
library(tseries)
library(fGarch)
library(PEIP)
library(tidyverse)
library(gridExtra)
library(gdata)
library(xtable)
library(vioplot)
library(moments)
```

\section{Download the data}

```{r}
# Set start and end date of data to download
dateStart <- "2017-10-01"             # Starting date of ADA-USD (latest)  
dateEnd <- "2021-11-26"               # sdate3 <- "12-15-2001"

startD=as.Date(dateStart, "%Y-%m-%d") # date <- as.Date(date, "%m-%d-%Y"); ndate3
startD
endD=as.Date(dateEnd, "%Y-%m-%d")

sprintf("We consider %d days", endD-startD)

# Bitcoin USD (BTC-USD) 
BTC <- get.hist.quote(instrument="BTC-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

# Ether cryptocurrency
ETH <- get.hist.quote(instrument="ETH-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

# BinanceCoin Cryptocurrency
BNB <- get.hist.quote(instrument="BNB-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

## Rippe (XRP) cryptocurrency
XRP <- get.hist.quote(instrument="XRP-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

# Dogecoin USD (DOGE-USD)
DOGE <- get.hist.quote(instrument="DOGE-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

# Cardano Cryptocurrency
ADA <- get.hist.quote(instrument="ADA-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
                        retclass="zoo")

# Tether - Stablecoin token on Ethereum blockchain
# USDT <- get.hist.quote(instrument="USDT-USD",start = dateStart, end=dateEnd,quote = c("AdjClose"),
#                         retclass="zoo")

## We missed Solana - as it did not have 1000 daily data points(started in Jul-2020)



### Plot the five datasets to understand the basics.
data <- merge(BTC,ETH,BNB,XRP,DOGE,ADA) # price data
head(data)
tail(data)

# Identify and remove missing value
sum(is.na(data))
index(data[is.na(data)])
data1 <- na.omit(data)   # Apply na.omit function
sum(is.na(data1))

# inspect the price data
# cat("Start: ", as.character(start(BITCOIN)), "  End: ", as.character(end(BITCOIN)))

names(data1)<-c("Price.BTC","Price.ETH","Price.BNB","Price.XRP","Price.DOGE","Price.ADA")


return.cc = diff(log(data1))
ret.cc<-as.data.frame(tail(return.cc, nrow(return.cc))) # all possible observations we can have for the cryptos
p <- seq(0.001, 0.01, 0.0001) # p for VaR
main.names<-c("BTC","ETH","BNB","XRP","DOGE","ADA")
nrow(return.cc) # We have maximum 1480 data points in return.cc

n_test = floor((1/3)* nrow(ret.cc)) ## size of testing data
n_train = nrow(ret.cc) - n_test
```


```{r}
# sample correlation
rho.cal<-function(X){
  rho.hat<-cor(sign(X-mean(X)), X-mean(X))
  return(rho.hat)
}

# Volatility correlation
rho.vol<-function(X){
  rho.vol<-cor(abs(X-mean(X)), (X-mean(X))^2)
  return(rho.vol)
}

# # skewness correlation
# skewrho <- function(X){
#   skewrho.cor <- cor(X-mean(X), (X-mean(X))^2)
#   return(skewrho.cor)
# }


ret.0.cc<-ret.cc
for(j in 1:ncol(return.cc)){
  ret.0.cc[, j]<-ret.cc[, j]-mean(ret.cc[, j]) # This is the centered log returns
}

rho<-apply(as.matrix(ret.0.cc), MARGIN=2, FUN=rho.cal)
rhov<-apply(as.matrix(ret.0.cc), MARGIN=2, FUN=rho.vol)


corrdisplay=data.frame(rho,rhov)
colnames(corrdisplay)=c("sign-corr","Vol-corr")
corrdisplay

```


```{r}
# calculate degree of freedom
# PEIP package is used here for uniroot function
nu<-rep(0, ncol(return.cc)) 
for(i in 1:ncol(return.cc)){
  fun <- function (x) rho[i]*(x-1)*beta(x/2,1/2)-2*sqrt(x-2)
  nu[i] <- uniroot(fun, c(2, 8))$root
}

# nuv<-rep(0, ncol(return.cc))
# for(i in 1:ncol(return.cc)){
#   fun <- function (x) rhov[i]*(x-1)*beta(x/2,1/2)-2*sqrt(x-2)
#   nuv[i] <- uniroot(fun,c(2,8))$root
# }

number<-ncol(data)
# Finding ACF
acf.s<-rep(0, number)  # ACF of the log returns
acf.abs<-rep(0, number) # ACF of the absolute returns
acf.sq<-rep(0, number) # ACF of the squared returns
for(j in 1:number){
  acf.s[j]<-acf(ret.0.cc[, j], plot=FALSE)$acf[2]
  acf.abs[j]<-acf(abs(ret.0.cc[, j]), plot=FALSE)$acf[2]
  acf.sq[j]<-acf(ret.0.cc[, j]^2, plot=FALSE)$acf[2]
}
corr<-data.frame(apply(ret.cc, 2, mean), apply(ret.cc, 2, sd), 
                 apply(ret.cc, 2, kurtosis),apply(ret.cc, 2, skewness),acf.s, acf.abs, 
                 acf.sq, rho, nu,rhov)
rownames(corr)<-main.names
colnames(corr)<-c("mean", "sd","kurtosis","skewness","series", "abs", "sq", "sign-rho", "df","vol-rho")
corr
# require(xtable)
# xtable(corr, digits=4)
```


\section{Garch model}

```{r}
ret.0<-tail(ret.0.cc, 1000) #latest 1000 observations
##### normal garch
VaR_rateG=matrix(0, nrow=length(p), ncol=ncol(ret.0))
ES_rateG=matrix(0, nrow=length(p), ncol=ncol(ret.0))
sigma_rate=c()
omega=c()
alpha=c()
beta=c()
for (j in 1:ncol(ret.0))
{
  g = garchFit(~garch(1,1),ret.0[,j],cond.dist="norm",include.mean=FALSE,
               trace=FALSE)
  omega[j] = g@fit$matcoef[1,1]
  alpha[j] = g@fit$matcoef[2,1]
  beta[j] = g@fit$matcoef[3,1]
  sigma_rate[j] =  omega[j] + alpha[j] * ret.0.cc[,j][T]^2 + beta[j] * g@h.t[T]
  for(i in 1:length(p)){
  VaR_rateG[i,j] = -sqrt(sigma_rate[j]) * qnorm(p[i]) * 1000
  ES_rateG[i,j] = -sqrt(sigma_rate[j])*integrate(function(q){q*dnorm(q)},-Inf,qnorm(p[i]))$value/(p[i]) * 1000
  }
}
```


```{r}
####### t garch
VaR_ratetG1=matrix(0, nrow=length(p), ncol=ncol(ret.0))
sigma_rate=c()
omega=c()
alphaG=c()
beta=c()
ES_ratetG1=matrix(0, nrow=length(p), ncol=ncol(ret.0))
dfG=c()
for (j in 1:ncol(ret.0))
{
  g = garchFit(~garch(1,1),ret.0[,j],cond.dist="std",include.mean=FALSE,
               trace=FALSE)
  omega[j] = g@fit$matcoef[1,1]
  alphaG[j] = g@fit$matcoef[2,1]
  beta[j] = g@fit$matcoef[3,1]
  dfG[j]=g@fit$matcoef[4,1]
  sigma_rate[j] =  omega[j] + alpha[j] * ret.0[,j][T]^2 + beta[j] * g@h.t[T]
  for(i in 1:length(p)){
    VaR_ratetG1[i,j] =(-1)* qstd (p[i], mean = 0, sd = sqrt(sigma_rate[j]), nu = dfG[j])*1000  
  # using fGarch package to get df
  ES_ratetG1[i,j] = sqrt(sigma_rate[j])*sqrt((dfG[j]-2)/dfG[j])*dt(qt (p[i],dfG[j]), dfG[j])/p[i]*(dfG[j] + (qt (p[i],dfG[j]))^2)/(dfG[j]-1)*1000}
}
VaR_ratetG1[91,]

# Error in solve.default(fit$hessian) : 
#   system is computationally singular: reciprocal condition number = 1.10481e-16
```


\section{Data Driven method}

\subsection{Choosing optimal value of lambda and alpha_e}

```{r}
# We are using all observations here and part of it as testing and part of it as training data
ret.0.cc<-as.data.frame(ret.cc)
for(j in 1:ncol(ret.cc)){
  ret.0.cc[, j]<-ret.cc[, j]-mean(ret.cc[,j])
}
```


\subsection{Choosing optimal alpha of Data Driven method}

```{r}
alpha.choose<-function(ret.cen, alpha=seq(0.01, 0.3, 0.01), cut.t){
  rho<-rho.cal(ret.cen)
  # rhov<-rho.vol(ret.cen)
  vol<-abs(ret.cen)/rho # Now we are smoothing abs(ret.cen)/rho , assuming symmetry
  t<-length(ret.cen) 
  MSE_alpha<-rep(0, length(alpha))
  for(a in 1:length(alpha)){
    s<-mean(vol[1:cut.t])
    error<-rep(0, t)
    for(i in 1:t){
      error[i]<-vol[i]-s
      s<-alpha[a]*vol[i]+(1-alpha[a])*s
    }
    MSE_alpha[a]<-mean(error[-(1:cut.t)]^2)
  }
  rmse<-sqrt(min(MSE_alpha))
  alpha.opt<-alpha[which.min(MSE_alpha)]
  return(c(rmse, alpha.opt))
}

```


```{r}


alpha.opt<-rep(0, number)
rmse.usual<-rep(0, number)
for(num in 1:number){
  result<-alpha.choose(ret.0.cc[, num], seq(0.01, 0.3, 0.01), n_train)
  alpha.opt[num]<-result[2]
  rmse.usual[num]<-result[1]
}
alpha.opt;rmse.usual # In Stat - smoothing statistics, in CS tuning parameter

```


\subsection{Choosing optimal omega and lambda for elastic method}


```{r}
# Check with original paper and equations
rmse.elastic.cal<-function(ret.cen, alpha, omega, lambda, cut.t){
  rho<-rho.cal(ret.cen)
  # rhov<-rho.vol(ret.cen)
  vol<-abs(ret.cen)/rho
  # vol.sub<-vol-sd(ret.cen)
  s<-mean(vol[1:cut.t])
  sd.r<-sd(ret.cen)
  if(abs(s-sd.r)>=omega*lambda)  
    s.elastic<- sign(s-sd.r)*(abs(s-sd.r)-omega*lambda)/(1+(1-omega)*lambda)+sd.r
   else s.elastic<-sd.r
  t<-length(ret.cen)
  error<-rep(0, t)
  for(i in 1:t){
    error[i]<-vol[i]-s.elastic
    s<-alpha*vol[i]+(1-alpha)*s
    if(abs(s-sd.r)>=omega*lambda)  
      s.elastic<-sign(s-sd.r)*(abs(s-sd.r)-omega*lambda)/(1+(1-omega)*lambda)+sd.r
    else s.elastic<-sd.r
  }
  rmse<-sqrt(mean(error[-(1:cut.t)]^2))
  return(rmse)
}
```


```{r}
lambda<-seq(0, 0.004, 0.0002)
omega<-seq(0, 1, 0.1)
rmse.elastic.opt<-rep(0, number)
omega.opt<-rep(0, number)
lambda.opt<-rep(0, number)
for(num in 1:number){
  rmse.elastic<-matrix(0, nrow=length(omega), ncol=length(lambda))
  for(a in 1:length(omega)){
    for(l in 1:length(lambda)){
      rmse.elastic[a, l]<-rmse.elastic.cal(ret.0.cc[, num], alpha.opt[num], 
                                           omega[a], lambda[l], n_train) 
    }
  }
  index.o<-which.min(apply(rmse.elastic, 1, min))
  index.l<-which.min(apply(rmse.elastic, 2, min))
  omega.opt[num]<-omega[index.o]
  lambda.opt[num]<-lambda[index.l]
  rmse.elastic.opt[num]<-rmse.elastic[index.o, index.l]
}
omega.opt; lambda.opt
rmse.elastic.opt
```


\subsection{Based on optimal alpha, alpha.e, lambda forecast the future value}


```{r}
vol.forecast<-function(ret.cen, alpha, omega, lambda, cut.t){
  rho<-rho.cal(ret.cen)
  # rhov<-rho.vol(ret.cen)
  vol<-abs(ret.cen)/rho
  sd.r<-sd(ret.cen)
  t<-length(ret.cen)
  res<-rep(0, t)
  res.elastic<-rep(0, t)
  s<-mean(vol[(1:cut.t)])
  s.elastic<-sign(s-sd.r)*max((abs(s-sd.r)-
               omega*lambda), 0)/(1+(1-omega)*lambda)+sd.r
  fore<-rep(0, t)
  fore.elastic<-rep(0, t)
  for(i in 1:t){
    res[i]<-ret.cen[i]/s
    res.elastic[i]<-ret.cen[i]/s.elastic
    fore[i]<-s
    fore.elastic[i]<-s.elastic
    s<-alpha*vol[i]+(1-alpha)*s
    s.elastic<-sign(s-sd.r)*
              max((abs(s-sd.r)-omega*lambda), 0)/(1+(1-omega)*lambda)+sd.r
  }
  fore.vol<-s
  fore.vol.elastic<-s.elastic
  return(list(fore.vol, fore.vol.elastic, res, res.elastic, fore, fore.elastic))
}
```


```{r}
forecast.vol<-rep(0, number)
forecast.vol.elastic<-rep(0, number)
res<-ret.0.cc
res.elastic<-ret.0.cc
fore.vary<-ret.0.cc
fore.elastic.vary<-ret.0.cc
for(num in 1:number){
  result<-vol.forecast(ret.0.cc[, num], alpha.opt[num], omega.opt[num], 
                       lambda.opt[num], n_train) ## 2/3 of 1480(total rows)
  forecast.vol[num]<-result[[1]]
  forecast.vol.elastic[num]<-result[[2]]
  res[, num]<-result[[3]]
  res.elastic[, num]<-result[[4]]
  fore.vary[, num]<-result[[5]]
  fore.elastic.vary[, num]<-result[[6]]
}
forecast.vol; forecast.vol.elastic
```


```{r}


vol.obs<-ret.0.cc
for(num in 1:number){
  vol.obs[, num]<-abs(ret.0.cc[, num])/rho[num]
}
for(num in 1:number){
  plot(1:n_test, tail(vol.obs[, num], n_test), xlab="t", ylab="vol", main=main.names[num], lwd=3,
       col="yellow", type="l")
  lines(1:n_test, tail(fore.vary[, num], n_test), col="blue", lwd=5)
  lines(1:n_test, tail(fore.elastic.vary[, num], n_test), col="purple")
  abline(h=sd(ret.0.cc[, num]), lty=3, col="red", lwd=3)
  legend("top",legend=c("vol", "NP", "Elastic", "sd"), col=c("yellow", "blue", "black", "red"),
         lty=c(1, 1, 1, 3), lwd=c(3, 5, 1, 3), cex=0.7)
}
for(num in 1:number){
  plot(1:n_test, tail(vol.obs[, num], n_test), xlab="t", ylab="vol", main=main.names[num], lwd=3,
       col="yellow", type="l")
  # lines(1:n_test, tail(fore.vary[, num], n_test), col="blue", lwd=5)
  lines(1:n_test, tail(fore.elastic.vary[, num], n_test), col="purple")
  abline(h=sd(ret.0.cc[, num]), lty=3, col="red", lwd=3)
  legend("top",legend=c("vol",  "Elastic", "sd"), col=c("yellow", "black", "red"),
         lty=c(1, 1, 1, 3), lwd=c(3, 5, 1, 3), cex=0.7)
}
for(num in 1:number){
  plot(1:n_test, tail(fore.vary[, num], n_test), col="green", lwd=5, type="l")
  lines(1:n_test, tail(fore.elastic.vary[, num], n_test), col="purple", lwd=4)
  abline(h=sd(ret.0.cc[, num]), lty=3, col="red", lwd=3)
  legend("top",legend=c( "NP", "Elastic", "sd"), col=c( "green", "purple", "red"),
         lty=c(1, 1, 3), lwd=c( 5, 1, 3), cex=0.7)
}


```


```{r}
vol.CI<-matrix(0, nrow=number, ncol=2)
vol.CI.elastic<-matrix(0, nrow=number, ncol=2)
for(i in 1:number){
  vol.CI[i, ]<-c(forecast.vol[i]+qnorm(0.05, 0, 1)*rmse.usual[i]/sqrt(n_test),
                 forecast.vol[i]+qnorm(0.95, 0, 1)*rmse.usual[i]/sqrt(n_test))
  vol.CI.elastic[i, ]<-c(forecast.vol.elastic[i]+qnorm(0.05, 0,1)*rmse.elastic[i]/sqrt(n_test),
                       forecast.vol.elastic[i]+qnorm(0.95, 0, 1)*rmse.elastic[i]/sqrt(n_test))
}

```


\subsection{Caculation of VaR and ES}

```{r}
scale.p<-function(nu, p) sqrt((nu-2)/nu)*dt(qt (p,nu), nu)/p*(nu + (qt (p,nu))^2)/(nu-1)
```


\subsubsection{Marginal}

```{r}
VaR.dd<-matrix(0, nrow=length(p), ncol=number)
ES.dd<-matrix(0, nrow=length(p), ncol=number)
VaR.dd.elastic<-matrix(0, nrow=length(p), ncol=number)
ES.dd.elastic<-matrix(0, nrow=length(p), ncol=number)
for(num in 1:number){
  for(i in 1:length(p)){
    VaR.dd[i, num]<-forecast.vol[num]*qstd(p=p[i], nu=nu[num])*(-1000)
    VaR.dd.elastic[i, num]<-forecast.vol.elastic[num]*qstd(p=0.01, nu=nu[num])*(-1000)
    ES.dd[i, num]<-forecast.vol[num]*scale.p(nu[num], p[i])*1000
    ES.dd.elastic[i, num]<-forecast.vol.elastic[num]*scale.p(nu[num], p[i])*1000
  }
}
VaR.dd[91,]; VaR.dd.elastic[91, ]
ES.dd[91, ]
no.penalty<-data.frame(alpha.opt, rmse.usual, forecast.vol,(t(VaR.dd)[,91]), (t(ES.dd)[,91]) )
colnames(no.penalty)<-c("alpha.opt", "RMSE", "Volatility", "VaR", "ES")
rownames(no.penalty)<-main.names
xtable(no.penalty, digits=6)
penalty<-data.frame(omega.opt, lambda.opt,rmse.elastic.opt, forecast.vol.elastic,
                    t(VaR.dd.elastic)[, 91],(t(ES.dd.elastic)[,91]))
colnames(penalty)<-c("omega.opt", "lambda.opt","RMSE", "Volatility", "VaR", "ES")
rownames(penalty)<-main.names
# xtable(penalty, digits=6)
penalty
```


```{r}
VaR.dd.CI.m<-matrix(0, nrow=number, ncol=4)
ES.dd.CI.m<-matrix(0, nrow=number, ncol=4)
for(num in 1:number){
  VaR.dd.CI.m[num, 1:2]<-(-1000)*qstd(p=0.01, nu=nu[num])*vol.CI[num,]
  VaR.dd.CI.m[num, 3:4]<-(-1000)*qstd(p=0.01, nu=nu[num])*vol.CI.elastic[num, ]
  ES.dd.CI.m[num, 1:2]<-(1000)*scale.p(nu[num], 0.01)*vol.CI[num, ]
  ES.dd.CI.m[num, 3:4]<-(1000)*scale.p(nu[num], 0.01)*vol.CI.elastic[num, ]
}
```


\subsubsection{Hybrid model}


```{r}
rho.res<-apply(res, 2, rho.cal)
rho.res.elastic<-apply(res.elastic, 2, rho.cal)
nu.res<-rho.res
nu.res.elastic<-rho.res.elastic
for(num in 1:number){
  fun <- function (x) rho.res[num]*(x-1)*beta(x/2,1/2)-2*sqrt(x-2)
  nu.res[num] <- uniroot(fun, c(2, 8))$root
  fun <- function (x) rho.res.elastic[num]*(x-1)*beta(x/2,1/2)-2*sqrt(x-2)
  nu.res.elastic[num] <- uniroot(fun, c(2, 8))$root
}
nu.res.elastic
nu.res
VaR.dd.res<-matrix(0, nrow=length(p), ncol=number)
ES.dd.res<-matrix(0, nrow=length(p), ncol=number)
VaR.dd.elastic.res<-matrix(0, nrow=length(p), ncol=number)
ES.dd.elastic.res<-matrix(0, nrow=length(p), ncol=number)
for(num in 1:number){
  for(i in 1:length(p)){
    VaR.dd.res[i, num]<-forecast.vol[num]*qstd(p=p[i], nu=nu.res[num])*(-1000)
    VaR.dd.elastic.res[i, num]<-forecast.vol.elastic[num]*qstd(p=p[i], nu=nu.res.elastic[num])*(-1000)
    ES.dd.res[i, num]<-forecast.vol[num]*scale.p(nu.res[num], p[i])*1000
    ES.dd.elastic.res[i, num]<-forecast.vol.elastic[num]*scale.p(nu.res.elastic[num], p[i])*1000
  }
}
nu.res
VaR.dd.elastic.res[91,]
ES.dd.elastic.res[91,]
```


```{r}
VaR.dd.CI.res<-matrix(0, nrow=number, ncol=4)
ES.dd.CI.res<-matrix(0, nrow=number, ncol=4)
for(num in 1:number){
  VaR.dd.CI.res[num, 1:2]<-(-1000)*qstd(p=0.01, nu=nu.res[num])*vol.CI[num,]
  VaR.dd.CI.res[num, 3:4]<-(-1000)*qstd(p=0.01, nu=nu.res.elastic[num])*vol.CI.elastic[num, ]
  ES.dd.CI.res[num, 1:2]<-(1000)*scale.p(nu.res[num], 0.01)*vol.CI[num, ]
  ES.dd.CI.res[num, 3:4]<-(1000)*scale.p(nu.res.elastic[num], 0.01)*vol.CI.elastic[num, ]
}
VaR.CI<-data.frame(VaR.dd.CI.m[, 1:2], VaR.dd.CI.res[, 1:2],
                   VaR.dd.CI.res[, 3:4], VaR.dd.CI.res[, 3:4])
xtable(VaR.CI)
ES.CI<-data.frame(ES.dd.CI.m[, 1:2], ES.dd.CI.res[, 1:2],
                   ES.dd.CI.res[, 3:4], ES.dd.CI.res[, 3:4])
rownames(ES.CI)<-main.names
xtable(ES.CI)
```

\subseciton{summary of result}

```{r}
table.usual<-data.frame(alpha.opt, rmse.usual, forecast.vol, VaR.dd[length(p),], ES.dd[length(p),])
table.elastic<-data.frame(omega.opt, rmse.elastic.opt, forecast.vol.elastic, VaR.dd.elastic[length(p), ], ES.dd.elastic[length(p),])
```


\section{Model risk summary}

```{r}
model.risk.VaR <-matrix(0, ncol=number, nrow=length(p))
model.risk.ES <-matrix(0, ncol=number, nrow=length(p))
for(num in 1:number){
  VaR<-data.frame(VaR_rateG[, num], VaR_ratetG1[, num], VaR.dd[, num], VaR.dd.res[, num])
  ES<-data.frame(ES_rateG[, num], ES_ratetG1[, num], ES.dd[, num], ES.dd.res[, num])
  model.risk.VaR[, num]<-apply(VaR, 1, max)/apply(VaR, 1, min)
  model.risk.ES[, num]<-apply(ES, 1, max)/apply(ES, 1, min)
}
```


```{r}
model.risk.VaR.elastic<-matrix(0, ncol=number, nrow=length(p))
model.risk.ES.elastic <-matrix(0, ncol=number, nrow=length(p))
for(num in 1:number){
  VaR<-data.frame(VaR_rateG[, num], VaR_ratetG1[, num], VaR.dd.elastic[, num], VaR.dd.elastic.res[, num])
  ES<-data.frame(ES_rateG[, num], ES_ratetG1[, num], ES.dd.elastic[, num], ES.dd.elastic.res[, num])
  model.risk.VaR.elastic[, num]<-apply(VaR, 1, max)/apply(VaR, 1, min)
  model.risk.ES.elastic[, num]<-apply(ES, 1, max)/apply(ES, 1, min)
}
```


\section{Model Risk calculations}


```{r}

MR_report <- data.frame(model.risk.VaR[91,], model.risk.ES[91,], model.risk.VaR.elastic[91,], model.risk.ES.elastic[91,])
rownames(MR_report)<-main.names

colnames(MR_report) <- c('VaR', 'ES', 'VaR Reg', 'ES Reg')
print(xtable(MR_report))

```


